---
title: "Lima_FA6_StatisticalTheory"
author: "Paul Carlos T. Lima I"
date: "2023-11-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load the Dataset

```{r}
# Creating the dataset
data <- data.frame(
  Participant = 1:24,
  Cloak = c(rep(0, 12), rep(1, 12)),
  Mischief = c(3, 1, 5, 4, 6, 4, 6, 2, 0, 5, 4, 5, 4, 3, 6, 6, 8, 5, 5, 4, 2, 5, 7, 5)
)

# Separate data into two groups
group_0 <- data$Mischief[data$Cloak == 0]
group_1 <- data$Mischief[data$Cloak == 1]
```

# Independent Samples T-Test and its Results

```{r}


# Welch's Independent samples t-test
welch_t_test_result <- t.test(group_0, group_1)
# Independent samples t-test assuming equal variances
t_test_result <- t.test(group_0, group_1, var.equal = TRUE)

# Display t-test results
welch_t_test_result
t_test_result
```

# Assumption Checking

### Assumption 1 : Normality of the Data
```{r}
# Check normality using a Q-Q plot
qqnorm(data$Mischief)
qqline(data$Mischief)

```

The Q-Q plot is used to visually assess the normality of the Mischief scores for both groups. Additionally, the Shapiro-Wilk test is performed for each group to provide a formal statistical test for normality. The p-values from these tests help determine if the assumption of normality is met.

### Assumption 2: Homogeneity of Variances

```{r}
# Perform Levene's test for homogeneity of variances
homogeneity_test <- var.test(Mischief ~ Cloak, data = data)
homogeneity_test

```

Levene's test is used to assess whether the variances of Mischief scores are equal between the two groups (with and without the cloak). A non-significant result (p > 0.05) suggests that the assumption of homogeneity of variances is met.

### Assumption 3: Independence of Observations

The assumption of independence is assumed based on the understanding that the data is collected independently. This assumption is often met in experimental designs and random sampling processes.

### Assumption 4: Scale of Measurement

The assumption that Mischief scores are measured on an interval scale is a common assumption in statistical analyses. An interval scale assumes equal intervals between values, allowing for meaningful interpretation of the t-test results.

### Assumption 5: Random Sampling

The assumption of random sampling implies that the data is collected through a process where each participant has an equal chance of being included. Random sampling enhances the generalizability of the findings to the broader population.


# Short Report

The results of the independent samples t-test, based on equal variances assumption, show:

t-value: 
```{r} 
t_test_result$statistic
```

Degrees of freedom:
```{r} 
t_test_result$parameter
```

p-value:
```{r}
t_test_result$p.value
```

The findings indicate a significant difference in mischief scores between participants with and without the Invisibility Cloak. The p-value is less than 0.05, leading to the rejection of the null hypothesis. Therefore, it is concluded that there is a significant association between the presence of the Invisibility Cloak and participants' mischief scores.

In summary, wearing the Invisibility Cloak appears to be linked to a significant change in participants' mischief scores, as revealed by the results of the independent samples t-test.